Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-17 tex/sections/consensus.tex
Add a new version of emergency forking
The algorithm still is a draft.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The recovery protocol can recover the functionality
of the Argennon blockchain as long as more than 2/3 of the total stake of the system is controlled by honest users
and any network partition resolves after a finite amount of time. The recovery protocol uses two main emergency
procedures to recover the functionality of the Argennon blockchain: \emph{emergency forking} and \emph{emergency
agreement} protocol.

@@

The reserve committee of delegates is able to fork the Argennon blockchain, if it receives a valid fork request
from the validators.
This fork needs to be confirmed by validators and can not discard any blocks that has been already certified
by validators.
A valid fork request is an unexpired request signed by more than half of the
total \texttt{online} stake of the validators.

For forking at block $b$, the reserve committee of delegates
makes a special \emph{fork block} which only contains a valid fork request, and its parent is the block $b$.
The height of the fork block is
$b + 1$ so it needs a valid certificate from the committee of validator with the index $b+1$ modulo $m$.

For signing a fork block, a validator ensures that the block is signed by the reserve committee and contains
a valid fork request. The parent of the fork block does not necessarily need a validators' certificate. If the
parent does not have a certificate, the validator checks the certificate of the block before the parent and
the conditional validity of the parent instead. This enables the reserve committee
to recover the liveliness of
the blockchain in a situation where a malicious committee has generated multiple blocks at the same height.

A validator always chooses a valid fork block over a block of the main chain. However, as we mentioned before,
a validator never signs a certificate for two different blocks with the same height. Consequently, if a validator
has already signed the block $b$ of the main chain, he will not sign the fork block and vice versa.

When the fork block is broadcast, it is possible that the validators of the committee with index $b+1$ modulo $m$
get divided between the fork block and the block $b+1$ of the main chain, in a way that no block gets enough validators.
This will cause the blockchain to halt. To prevent this, the protocol allows the reserve delegates to revoke a
fork block. After a fork block
is revoked, the validators who voted for it are allowed to vote for another block with the same
height.

To revoke a fork block with height $b+1$, the delegates need to seal the fork by adding a special
\emph{seal block} after the fork block.\footnote{The parent of the seal block must be the fork block.} The seal block
has the height $b+2$ and needs to be certified by the validators' committee with the
index $b+2$ modulo $m$. The fork block is considered revoked only after the seal block is certified by the validators.

The seal block is not a normal block and validators who signed a certificate for a seal block are allowed
to sign a certificate for a block with the same height and vice versa. However, it should be noted that
generating a block with the same parent as the seal block is considered a malicious behaviour of the reserve
committee and validators will not sign such a block.

As long as more than half of the total online stake of every committee of validators is controlled
by honest users, a malicious committee of delegates can not use the emergency forking procedure to discard blocks
that have a certificate from validators.

@@

@@

A user executes the following procedure
in round $r$ of the voting phase:
\paragraph{Voting Phase:}
\begin{itemize}
    \item if the user has not yet final-voted any value, he $r$-votes a single desired proposal.
    \item if he sees more than 2/3 $r$-votes for a proposal $p$, he final-votes $p$.
    \item if he sees more than 2/3 final-votes for a proposal, he goes to the confirmation phase for $p$.
    \item if $clock > r \cdot \lambda$ and $r < k$ user goes to the round $r + 1$ and if $r = k$ user starts a
    new agreement session.
\end{itemize}
\paragraph{Confirmation Phase for Proposal $p$:}
\begin{itemize}
    \item user c-votes $p$.
    \item if he sees more than 2/3 c-votes for $p$ he selects $p$ and ends the agreement protocol.
    \item if $clock > k \cdot \lambda$ user starts a new agreement session.
\end{itemize}

>>>>

The recovery protocol can recover the functionality
of the Argennon blockchain as long as more than $2/3$ of the total stake of the system is controlled by honest users
and any network partition resolves after a finite amount of time. The recovery protocol uses two main emergency
procedures to recover the functionality of the Argennon blockchain: \emph{emergency forking} and \emph{emergency
agreement} protocol.

@@

The reserve committee of delegates is able to fork the Argennon blockchain, if it receives a valid fork request
from the validators.
This fork needs to be confirmed by validators and can not discard any blocks that has been already certified
by validators.
A valid fork request is an unexpired request signed by more than half of the total stake of validators.

For forking at block $h$, the reserve committee of delegates
makes a special \emph{fork block} which only contains a valid fork request, and its parent is the block $h$.
The height of the fork block therefore is
$h + 1$, so it needs a valid certificate from the assembly of validators with the index $h+1$ modulo $m$.

For signing a fork block, a validator ensures that the block is signed by the reserve committee, contains
a valid fork request and its parent is not issued by the same reserve committee. The parent of the fork block does not
necessarily need a validators certificate. If the parent does not have a certificate, the validator checks the
certificate of the block before the parent and the conditional validity of the parent instead. This enables the
reserve committee to recover the liveliness of the blockchain in a situation where a malicious committee has
generated multiple blocks at the same height. Notice that the block before the parent always need a validators
certificate.

A validator always chooses a valid fork block over a block of the main chain. However, as we mentioned before,
a honest validator \textbf{never signs a certificate for two different blocks with the same height}. Consequently, if a
validator has already signed the block $h+1$ of the main chain, he will not sign the fork block at height $h+1$ and
vice versa.

The reserve committee of delegates is not allowed to generate multiple fork blocks at the same height. However, they
can generate multiple fork blocks with different heights, as long as the parent block is generated by the previous
committee. When the reserve committee generates a fork block at height $h+1$, but the block fails to receive a
certificate from validators, the committee will generate a new fork block at height $h+2$.

@@

\paragraph{Analysis}

When the reserve committee gets activated, the main committee might have been malicious, so any number of blocks could
exist at each height. However, at each height at max one block can have a validators certificate. Moreover, if at some
height there are not any blocks with a validators certificate, then no blocks at higher heights can have a
validators certificate, because validators do not sign the certificate of a normal block if its parent does
not have a certificate.

If $h_{\max}$ denotes the height of the highest block with a validators certificate and a fork block is generated at
height $h$, as long as more than $2/3$ stake of all the assemblies of validators are honest, we have:
\begin{itemize}
    \item if $h > h_{\max} + 2$, the fork block can not receive a certificate from validators.
    \item if $h = h_{\max} + 2$, the fork block can always receive a certificate from validators if network
    partitions do not last forever.
    \item if $h = h_{\max} + 1$, the fork block may receive a certificate from validators or not. It is possible that
    the validators of the assembly with index $h+1$ modulo $m$ get divided between the fork block and a block at
    height $h+1$ of the main chain.
    \item if $h < h_{\max} + 1$, the fork block can not receive a certificate from validators.
\end{itemize}

Obviously, if the reserve committee generates two fork blocks at height $h_{\max} + 2$ and $h_{\max} + 1$, both blocks
could receive a validators certificate. However, this will not be problematic, since when the fork block at height
$h_{\max} + 2$ has a validators certificate, any block added after the fork block at height $h_{\max} + 1$ can not
receive the certificate of validators and the fork block at this height is effectively sealed.

During the emergency forking, at max one block with a validators certificate may be discarded. This happens when
the malicious main committee of delegates has forked the main chain by producing blocks $b_1$ and $b_2$ at height
$h$; the block $b_1$ has received a validators certificate and validators have not certified any blocks at height $h+1$.
The reserve committee adds a fork block after block $b_2$ and that will discard $b_1$. Notice that if a block at
height $h+1$ had been certified by validators the fork block chould not have received a certificate from validators.

@@

A user executes the following procedure
in round $r$ of the voting phase:

\paragraph{Voting Phase:}
\begin{itemize}
    \item if the user has not yet final-voted any value, he $r$-votes a single desired proposal.
    \item if he sees more than 2/3 $r$-votes for a proposal $p$, he final-votes $p$.
    \item if he sees more than 2/3 final-votes for a proposal, he goes to the confirmation phase for $p$.
    \item if $clock > r \cdot \lambda$ and $r < k$ user goes to the round $r + 1$ and if $r = k$ user starts a
    new agreement session.
\end{itemize}

\paragraph{Confirmation Phase for Proposal $p$:}
\begin{itemize}
    \item user c-votes $p$.
    \item if he sees more than 2/3 c-votes for $p$ he selects $p$ and ends the agreement protocol.
    \item if $clock > k \cdot \lambda$ user starts a new agreement session.
\end{itemize}
